Unifying Lower Bounds on Prediction Dimension of Consistent Convex Surrogates

### 2021-05-20 cvx-flats-neurips21/cvx-flats.tex
meeting notes

\begin{abstract}
	\jessie{Revisit}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension which is simultaneously stronger and broader than previous results.
To understand how our framework for producing lower bounds is stronger, we introduce ``four quadrants'' of problem settings, and our bound holds for all four; previous bounds only apply to one quadrant at a time.
To demonstrate the strength of our bounds, we show new results for the prediction dimension required to estimate entropy and norms, answering an open problem of~\citet{frongillo2015elicitation}.

@@

We present a unification of existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
For type (2), we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question above.
Our framework rests on \emph{property elicitation}, a weaker condition than calibration, as a tool to understand consistency across a wide variety of domains.

>>>>

\begin{abstract}

  \raf{Notes}
  We present a new tool based on property elicitation to study the prediction dim of surrogate loss functions.
  Our tool unifies... including continuous vs discrete.
  New result in risk measures...
  FSD...

	\jessie{Revisit}
Given a prediction task, understanding when one can and cannot design a consistent convex surrogate loss, particularly a low-dimensional one, is an important and active area of machine learning research. 
The prediction task may be given as a target loss, as in classification and structured prediction, or simply as a (conditional) statistic of the data, as in risk measure estimation.
These two scenarios typically involve different techniques for designing and analyzing surrogate losses.
We unify these settings using tools from property elicitation, and give a general lower bound on prediction dimension which is simultaneously stronger and broader than previous results.
To understand how our framework for producing lower bounds is stronger, we introduce ``four quadrants'' of problem settings, and our bound holds for all four; previous bounds only apply to one quadrant at a time.
To demonstrate the strength of our bounds, we show new results for the prediction dimension required to estimate entropy and norms, answering an open problem of~\citet{frongillo2015elicitation}.

@@

We present a new tool, \emph{$d$-flats}, which unifies existing techniques to bound the prediction dimension of consistent convex surrogates in both settings above.
Using this tool, we give the first prediction dimension bounds for risk measures with respect to convex surrogates, addressing the open question for type (II) above.
In settings of type (I), $d$-flats recover and tighten the feasible subspace dimension result of \citet{ramaswamy2016convex}.
%In settings of type (I), $d$-flats give tighter bounds in some cases, e.g. feasible subspace dimension result of \citet{ramaswamy2016convex}.

% Applied to settings of type (1), we recover the feasible subspace dimension result of \citet{ramaswamy2016convex}, and give an example where our bound is even tighter.
Our framework rests on \emph{property elicitation}, a weaker and simpler condition than calibration, as a way to understand consistency across a wide variety of domains.
